Parsing Postfix log files

### 2009-01-09 doc/logparser-acronyms.tex
Converted from article to report, and sections to chapters. Some cleanups. @ doesn't need escaping in glossary entries with new glossaries package.

\newglossaryentry{MTA}{
    type=\acronymtype,
    name={MTA},
    description={Mail Transfer Agent\glsadd{MTA glossary}}
}
\newglossaryentry{MTA glossary}{
    name={Mail Transfer Agent},
    description={
        A Mail Transfer Agent sends and receives mail via
        SMTP\backslashat{}.  Users submit mail to an MTA via their mail
        client (e.g.\ Microsoft Outlook, Thunderbird, webmail services);
        the sending MTA transfers the mail to the receiving MTA (which may
        in turn forward it to another MTA).
    }
}

\newglossaryentry{RFC}{
    type=\acronymtype,
    name={RFC},
    description={Request For Comments\glsadd{RFC glossary}}
}
\newglossaryentry{RFC glossary}{
    name={Request For Comments},
    description={
        The Request For Comments series is a series of proposals defining
        various protocols and file formats, e.g.\ SMTP\backslashat{}.  The
        name is somewhat misleading: initially the authors were asking for
        peer review, but these documents are now the de facto standards the
        Internet runs on.
    }
}

>>>>

\newglossaryentry{MTA}{
    type=\acronymtype,
    name={MTA},
    description={Mail Transfer Agent\glsadd{MTA glossary}}
}
\newglossaryentry{MTA glossary}{
    name={Mail Transfer Agent},
    description={
        A Mail Transfer Agent sends and receives mail via SMTP\@.  Users
        submit mail to an MTA via their mail client (e.g.\ Microsoft
        Outlook, Thunderbird, webmail services); the sending MTA transfers
        the mail to the receiving MTA (which may in turn forward it to
        another MTA).
    }
}

\newglossaryentry{RFC}{
    type=\acronymtype,
    name={RFC},
    description={Request For Comments\glsadd{RFC glossary}}
}
\newglossaryentry{RFC glossary}{
    name={Request For Comments},
    description={
        The Request For Comments series is a series of proposals defining
        various protocols and file formats, e.g.\ SMTP\@.  The name is
        somewhat misleading: initially the authors were asking for peer
        review, but these documents are now the de facto standards the
        Internet runs on.
    }
}

### 2009-01-09 doc/logparser-glossary.tex
Minor cleanups.
Converted from article to report, and sections to chapters. Some cleanups. @ doesn't need escaping in glossary entries with new glossaries package.

% vim: set filetype=tex :
% The contents of the glossary.
\newglossaryentry{SQLite}{name={SQLite},description={
    \textit{SQLite is a small C library that implements a self-contained,
    embeddable, zero-configuration SQL database engine.\/} SQLite is an
    \gls{SQL} implementation focusing on correctness, simplicity and speed.
    Unlike other \gls{SQL} implementations it does not require a separate
    server process, greatly simplifying deployment of an application
    utilising it.  More details can be found
    at~\url{http://www.sqlite.org/}.
}}

@@

\newglossaryentry{<>}{name={$<>$},sort={<>},description={
    $<>$ is the sender address used for mail that should not be replied to,
    e.g.\ bounce notifications.  In \gls{SMTP} all addresses are enclosed
    in $<>$, so \textit{username\at{}domain\/} becomes
    \textit{$<$username\at{}domain$>$\/}; thus $<>$ is actually an empty
    address, but is always written as $<>$ for clarity.  All mail servers
    must accept mail sent from $<>$, or they are in violation of
    \gls{RFC}~2821~\cite{RFC2821}.
}}

@@

\newglossaryentry{mail loop}{name={mail loop},description={
    Sometimes mail sent to one address must be forwarded to a different
    address instead, e.g.\ because a person has changed jobs.  A mail loop
    occurs when the chain of recipient addresses constitute a cyclic
    directed graph; the simplest example is when mail for
    \texttt{alice\at{}example.net} is delivered to
    \texttt{bob\at{}example.com}, and mail for \texttt{bob\at{}example.com}
    is delivered to \texttt{alice\at{}example.net}.
}}

>>>>

% vim: set filetype=tex :
% The contents of the glossary.
\newglossaryentry{SQLite}{name={SQLite},description={
    \textit{SQLite is a small C library that implements a self-contained,
    embeddable, zero-configuration SQL database engine.\/} SQLite is an
    \gls{SQL} implementation focusing on correctness, simplicity, and
    speed.  Unlike other \gls{SQL} implementations it does not require a
    separate server process, greatly simplifying deployment of an
    application utilising it.  More details can be found
    at~\url{http://www.sqlite.org/}.
}}

@@

\newglossaryentry{<>}{name={$<>$},sort={<>},description={
    $<>$ is the sender address used for mail that should not be replied to,
    e.g.\ bounce notifications.  In \gls{SMTP} all addresses are enclosed
    in $<>$, so \textit{username@domain\/} becomes
    \textit{$<$username@domain$>$\/}; thus $<>$ is actually an empty
    address, but is always written as $<>$ for clarity.  All mail servers
    must accept mail sent from $<>$, or they are in violation of
    \gls{RFC}~2821~\cite{RFC2821}.
}}

@@

\newglossaryentry{mail loop}{name={mail loop},description={
    Sometimes mail sent to one address must be forwarded to a different
    address instead, e.g.\ because a person has changed jobs.  A mail loop
    occurs when the chain of recipient addresses constitute a cyclic
    directed graph; the simplest example is when mail for
    \texttt{alice@example.net} is delivered to \texttt{bob@example.com},
    and mail for \texttt{bob@example.com} is delivered to
    \texttt{alice@example.net}.
}}

### 2009-01-09 doc/logparser-introduction.tex
Converted from article to report, and sections to chapters. Some cleanups. @ doesn't need escaping in glossary entries with new glossaries package.

\section{Introduction}

@@

Appendix~XXX provides a glossary of terms used in the thesis.

Appendix~XXX provides a list of acronyms used in the thesis.

>>>>

\chapter{Introduction}

@@

Appendix~\ref{Glossary} provides a glossary of terms used in the thesis.

Appendix~\ref{Acronyms} provides a list of acronyms used in the thesis.

Appendix~\ref{Postfix Daemons} gives a brief description of Postfix
daemons.

### 2009-01-09 doc/logparser-postfix-daemons.tex
Converted from article to report, and sections to chapters. Some cleanups. @ doesn't need escaping in glossary entries with new glossaries package.

\newglossaryentry{virtual}{name={virtual},type={postfix},description={
    Virtual is the Postfix component responsible for delivery of mails to
    virtual domains.  With \daemon{local} delivery the destination is
    determined only by the portion of the email address on the left side of
    the \at{}, whereas with \daemon{virtual} delivery the destination is
    determined by the entire email address.  E.g.\ if the server is
    responsible for both the \textbf{example.org} and \textbf{example.net}
    domains: \daemon{local} considers \textbf{john\at{}example.org} and
    \textbf{john\at{}example.net} to have the same mailbox, whereas
    \daemon{virtual} considers them to have different mailboxes.  Virtual
    delivery is used when a server hosts multiple domains where a username
    may be present in more than one domain but represent different users in
    each.  The definitive documentation is
    \url{http://www.postfix.org/virtual.8.html}.
}}

>>>>

\newglossaryentry{virtual}{name={virtual},type={postfix},description={
    Virtual is the Postfix component responsible for delivery of mails to
    virtual domains.  With \daemon{local} delivery the destination is
    determined only by the portion of the email address on the left side of
    the @, whereas with \daemon{virtual} delivery the destination is
    determined by the entire email address.  E.g.\ if the server is
    responsible for both the \textbf{example.org} and \textbf{example.net}
    domains: \daemon{local} considers \textbf{john@example.org} and
    \textbf{john@example.net} to have the same mailbox, whereas
    \daemon{virtual} considers them to have different mailboxes.  Virtual
    delivery is used when a server hosts multiple domains where a username
    may be present in more than one domain but represent different users in
    each.  The definitive documentation is
    \url{http://www.postfix.org/virtual.8.html}.
}}

### 2009-01-09 doc/logparser.tex
Started updating blurbs etc. in the start of the art review. Dealt with a few XXX items.
Improved the appearance of URLs and notes in the bibliography.
Improvements after dry runs with Carl.
Some minor changes based on the SGAI paper.
Improvements to the glossaries appearance. Minor fixes.
Converted from article to report, and sections to chapters. Some cleanups. @ doesn't need escaping in glossary entries with new glossaries package.

% $Id$
\documentclass[a4paper,12pt,draft]{article}

% Useful stuff for math mode.
\usepackage{amstext}
% Include images
\usepackage[final]{graphicx}
% Add the bibliography into the table of contents.
\usepackage[section,numbib]{tocbibind}
% Create a label for the last page.  Might be useful for "page 23/79" or
% something.
\usepackage{lastpage}

% Extra packages recommended by Springer: they change the fonts from
% Computer Modern to something else and tells Latex to use scalable fonts.
\usepackage{type1cm}
%\usepackage{mathptmx}
%\usepackage{helvet}
%\usepackage{courier}
% Extra footnote functionality, including references to earlier footnotes.
\usepackage{footmisc}

@@

% Sort numbers where there are multiple citations.  Does not appear to have
% the expected effect (probably clashes with varioref or hyperref), though
% it does reduce the space between numbers.
\usepackage{cite}

@@

@@

% Provides commands to distinguish between pdf and dvi output.
\usepackage{ifpdf}
% When creating a \PDF{} make the table of contents into links to the pages
% (without horrible red borders) and include bookmarks.  The title and
% author do not work - I think either gnuplot or graphviz clobbers it.
% hyperfootnotes need to be disabled to avoid breaking footmisc, but they
% still seem to work, somehow.
\ifpdf{}
    \usepackage[pdftex,hyperfootnotes=false]{hyperref}
\else{}
    \usepackage[dvips,hyperfootnotes=false]{hyperref}
    % This is necessary for wrapping URLs in the bibliography when
    % producing a dvi, but causes problems when generating \PDF{} output.
    \usepackage{breakurl}
\fi{}
\hypersetup{
    pdftitle    = {Parsing Postfix log files},
    pdfauthor   = {John Tobin},
    final       = true,
    pdfborder   = {0 0 0},
}

% Acronyms and glossary entries.
\usepackage[acronym,toc,numberedsection]{glossaries}
\newglossary[plg]{postfix}{pin}{pout}{Postfix Daemons}
\makeglossaries{}

@@

% Show the citation key (e.g. slct-paper) in the margin beside the
% reference.
\usepackage[nomsgs]{refcheck}
% Show where references are used.
% Neither work.
%\usepackage{citeref}
%\usepackage{backref}
\renewcommand{\refname}{Bibliography}
% Add space before urls to quell underfull hbox warnings.
\newcommand{\urlprefix}[0]{\hfill{}}
% New formatting commands.

@@

%\showtable{filename}{caption}{label}
\newcommand{\showtable}[3]{%
    \begin{table}[ht]
        \caption{#2}\label{#3}
        \input{#1}
    \end{table}
}

\newcommand{\tableline}[0]{%
    \noalign{\smallskip}%
    \hline%
    \noalign{\smallskip}%
}

@@

% This is ridiculous, but I cannot put @ in glossary entries, so . . .
\newcommand{\at}[0]{%
    @%
}
% This is ridiculous, but I cannot put @ in glossary entries, so . . .
\newcommand{\backslashat}[0]{%
    \@%
}

@@

% The name of the program, so I only have to change it in one place.
\newcommand{\parsername}{\gls{PLP}}
\newcommand{\parsernames}{\gls{PLP}'s}

% This keeps hyperref fairly happy about the Abstract entry in the table of
% contents.
\newcounter{dummy}

@@

\title{Parsing Postfix log files}
\author{John Tobin \\ School of Computer Science and Statistics \\
Trinity College \\ Dublin 2 \\ Ireland \\ tobinjt@cs.tcd.ie}
\maketitle
\SVN$Id$
\begin{center}\SVNId{}\end{center}

\refstepcounter{dummy}
\addcontentsline{toc}{section}{Abstract}
\begin{abstract}

@@

@@

XXX WOULD TABLES LOOK BETTER IF CAPTIONS WERE LEFT-ALIGNED\@?

XXX REDUCE THE LIST OF ACRONYMS\@.

@@

XXX IMPROVE BIBLIOGRAPHY APPEARANCE\@: NAMES LOOK UGLY (E.G.\ P.\
\empty{}.\ Porters), URL SPACING IS MESSED UP --- URLS \\SHOULD PROBABLY BE
LAST, ON THEIR OWN LINE\@.

@@

%\bibliographystyle{logparser-bibliography-style}
\bibliographystyle{sgai-2008-elsevier}
\bibliography{logparser-bibliography}

% Redefine the command used to produce the glossary title, because the
% default command produces an unnumbered section whereas I want a numbered
% section.
%\renewcommand{\glossarytitle}{\section{Glossary}\label{Glossary}}
\label{Glossary}
\printglossaries{}
% Redefine the command a second time to produce acronyms instead of a
% glossary.
%\renewcommand{\glossarytitle}{\section{Acronyms}\label{Acronyms}}
%\printacronym{}

>>>>

% $Id$
\documentclass[a4paper,12pt,draft]{report}

% Useful stuff for math mode.
\usepackage{amstext}
% Include images
\usepackage[final]{graphicx}
\usepackage{url}
% Add the bibliography into the table of contents.
\usepackage[chapter,numbib]{tocbibind}
% Create a label for the last page.  Might be useful for "page 23/79" or
% something.
\usepackage{lastpage}

% Extra footnote functionality, including references to earlier footnotes.
\usepackage[bottom]{footmisc}
% The Euro symbol
\usepackage{eurofont}

@@

% Tell Latex to use scalable fonts
\usepackage{type1cm}

% Extra packages recommended by Springer.
%\usepackage{mathptmx}
%\usepackage{helvet}
%\usepackage{courier}
%\usepackage{makeidx}
%\usepackage{multicol}

@@

% Sort numbers where there are multiple citations.  Does not appear to have
% the expected effect (probably clashes with varioref or hyperref), though
% it does reduce the space between numbers.
\usepackage{cite}
% Check for unused references.
% \usepackage{refcheck}

@@

% Acronyms and glossary entries.  Useful options:
% * nonumberlist disables the list of page numbers after each entry.
\usepackage[acronym,toc,numberedsection=autolabel,style=list,nonumberlist]{glossaries}
\renewcommand{\glspostdescription}[0]{}
\renewcommand{\glsautoprefix}[1]{glossary:#1}
\newglossary[plg]{postfix}{pin}{pout}{Postfix Daemons}
\makeglossaries{}

% Provides commands to distinguish between pdf and dvi output.
\usepackage{ifpdf}
% When creating a \PDF{} make the table of contents into links to the pages
% (without horrible red borders) and include bookmarks.  The title and
% author do not work - I think either gnuplot or graphviz clobbers it.
% hyperfootnotes need to be disabled to avoid breaking footmisc, but they
% still seem to work, somehow.
\ifpdf{}
    \usepackage[pdftex,hyperfootnotes=false,plainpages=false,pdfpagelabels]{hyperref}
\else{}
    \usepackage[dvips,hyperfootnotes=false,plainpages=false,pdfpagelabels]{hyperref}
    % This is necessary for wrapping URLs in the bibliography when
    % producing a dvi, but causes problems when generating \PDF{} output.
    \usepackage{breakurl}
\fi{}
\hypersetup{
    pdftitle    = {Parsing Postfix log files},
    pdfauthor   = {John Tobin},
    final       = true,
    pdfborder   = {0 0 0},
}

@@

% Show the citation key (e.g. slct-paper) in the margin beside the
% reference.
%\usepackage[nomsgs]{refcheck}
% Show where references are used.
% Neither work.
%\usepackage{citeref}
%\usepackage{backref}
%\renewcommand{\refname}{Bibliography}
% Put each URL in the bibliography on a new line.
\newcommand{\urlprefix}[0]{\newline{}}
% New formatting commands.

@@

%\showtable{filename}{caption}{label}
\newcommand{\showtable}[3]{
    \begin{table}[ht]
        \caption{#2}\label{#3}
        \input{#1}
    \end{table}
}

\newcommand{\tabletopline}[0]{%
    \hline%
    \noalign{\smallskip}%
}

\newcommand{\tablebottomline}[0]{%
    \noalign{\smallskip}%
    \hline%
}

\newcommand{\tablemiddleline}[0]{%
    \noalign{\smallskip}%
    \hline%
    \noalign{\smallskip}%
}

@@

@@

% The name of the program, so I only have to change it in one place.
\newcommand{\parsername}{\gls{PLP}}
% XXX SHOULD THIS BE \glspl{PLP} or \gls{PLP}'s ??
\newcommand{\parsernames}{\glspl{PLP}}

@@

\title{Parsing Postfix log files}
\author{John Tobin \\ School of Computer Science and Statistics \\
Trinity College \\ Dublin 2 \\ Ireland \\ tobinjt@cs.tcd.ie}
\maketitle

\begin{abstract}

    \phantomsection{}
    \addcontentsline{toc}{chapter}{Abstract}

@@

\SVN$Id$
\begin{center}
    \SVNId{}
\end{center}

XXX WHY DOES \\ref{} NOT WORK PROPERLY FOR CHAPTERS IN THE APPENDIX\@?

@@

@@

XXX IMPROVE BIBLIOGRAPHY APPEARANCE\@: NAMES LOOK UGLY (E.G.\ P.\
\empty{}.\ Porters)\@.

XXX INVESTIGATE Doug Lenat.

@@

\bibliographystyle{logparser-bibliography-style}
\bibliography{logparser-bibliography}

\label{Glossary}
\printglossary{}
\label{Acronyms}
\printglossary[type=\acronymtype]{}
\label{Postfix Daemons}
\printglossary[type=postfix]{}
